Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing

### 2021-10-21 00-ES/PubliER/PubliER.Rmd
First real PPQS 21-10-2021-PPQS.pdf

## Distributed recycling via additive manufacturing

<!-- DRAM -->
Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management [@CruzSanchez2020; @Santander2020]. 
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches. 
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

\textcolor{red}{ To complete ...}

@@

## Planning

@@

# Case study: Distributing recycling via Additive Manufacturing
## Indicators in Ecosystem Services Distributed recycling The

\newpage

# Results of the

## Planning

### Goal and scope definition

The system depicted is presented in the figure.
The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped  by . 
Because Es are expected to be more relevant in the

>>>>

@@

# Results

## Step I - Definition the Industrial system : Distributed recycling via additive manufacturing

<!-- Distributed Fabrication -->
Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication

In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock [@CruzSanchez2020; @Santander2020]. 
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches. 
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

The system depicted is presented in the figure XX.
The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped  by . 
Because Es are expected to be more relevant in the

## Step II - Ecosystem services Priorities at the territorial level: Nancy, France

@@

## Step III - Ecosystem Services issues at the Value chain: Plastic issues at the ecosystems

## Step II - Identifying the Hot spot of the

# Discussion and perspective of the analysis

# Conclusions

### 2021-10-21 00-ES/PubliER/PubliER.tex
First real PPQS 21-10-2021-PPQS.pdf

\hypertarget{distributed-recycling-via-additive-manufacturing}{%
\subsection{Distributed recycling via additive manufacturing}\label{distributed-recycling-via-additive-manufacturing}}

Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al. 2020}; \protect\hyperlink{ref-Santander2020}{Santander et al. 2020}).
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

\textcolor{red}{ To complete ...}

@@

\hypertarget{planning}{%
\subsection{Planning}\label{planning}}

@@

\hypertarget{case-study-distributing-recycling-via-additive-manufacturing}{%
\section{Case study: Distributing recycling via Additive Manufacturing}\label{case-study-distributing-recycling-via-additive-manufacturing}}

\hypertarget{indicators-in-ecosystem-services-distributed-recycling-the}{%
\subsection{Indicators in Ecosystem Services Distributed recycling The}\label{indicators-in-ecosystem-services-distributed-recycling-the}}

\hypertarget{results-of-the}{%
\section{Results of the}\label{results-of-the}}

\hypertarget{planning-1}{%
\subsection{Planning}\label{planning-1}}

\hypertarget{goal-and-scope-definition}{%
\subsubsection{Goal and scope definition}\label{goal-and-scope-definition}}

The system depicted is presented in the figure.
The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped by .
Because Es are expected to be more relevant in the

>>>>

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{step-i---definition-the-industrial-system-distributed-recycling-via-additive-manufacturing}{%
\subsection{Step I - Definition the Industrial system : Distributed recycling via additive manufacturing}\label{step-i---definition-the-industrial-system-distributed-recycling-via-additive-manufacturing}}

Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication

In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al. 2020}; \protect\hyperlink{ref-Santander2020}{Santander et al. 2020}).
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

The system depicted is presented in the figure XX.
The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped by .
Because Es are expected to be more relevant in the

\hypertarget{step-ii---ecosystem-services-priorities-at-the-territorial-level-nancy-france}{%
\subsection{Step II - Ecosystem services Priorities at the territorial level: Nancy, France}\label{step-ii---ecosystem-services-priorities-at-the-territorial-level-nancy-france}}

@@

\hypertarget{step-iii---ecosystem-services-issues-at-the-value-chain-plastic-issues-at-the-ecosystems}{%
\subsection{Step III - Ecosystem Services issues at the Value chain: Plastic issues at the ecosystems}\label{step-iii---ecosystem-services-issues-at-the-value-chain-plastic-issues-at-the-ecosystems}}

\hypertarget{step-ii---identifying-the-hot-spot-of-the}{%
\subsection{Step II - Identifying the Hot spot of the}\label{step-ii---identifying-the-hot-spot-of-the}}

\hypertarget{discussion-and-perspective-of-the-analysis}{%
\section{Discussion and perspective of the analysis}\label{discussion-and-perspective-of-the-analysis}}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}
